---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("openintro")
suppressPackageStartupMessages(library(openintro))
suppressPackageStartupMessages(library(tidyverse))

```
#prelim
```{r}
fastfood <- openintro::fastfood
fastfood
```
#Q1 Looking only at Burger King and Chick-Fil-A, which item has the highest calories?  The answer should be saved as Q1.
```{r}
Q1<- fastfood %>% 
  filter(restaurant == 'Burger King' | restaurant == 'Chick Fil-A') %>% 
  arrange(desc(calories)) %>% 
  select(item) %>% 
  head(1)

Q1
```
#Q2 What is the mean sugar amount for all items from Subway?
```{r}
Q2<- fastfood %>% 
  filter(restaurant == 'Subway') %>% 
  summarise(mean_sugar = mean(sugar)) %>% 
  as.data.frame()

Q2
```

#Q3 What is the mean value of calories for all items from Taco Bell?
```{r}
Q3<- fastfood %>% 
  filter(restaurant == 'Taco Bell') %>% 
  summarise(mean_cal = mean(calories)) %>% 
  as.data.frame()

Q3
```

#Q4 Create a variable equal to total_fat x sugar called fatXsugar.  Produce a tibble that has the restaurant, item, and fatXsugar for the top 3 items, from highest to lowest.
```{r}
Q4<- fastfood %>% 
  mutate(fatXsugar=total_fat*sugar) %>%  
  arrange(desc(fatXsugar)) %>% 
  select(restaurant, item, fatXsugar) %>% 
  head(3)

Q4


```

#Q5 How many restaurants have an average saturated fat over 10?
```{r}
Q5<- fastfood %>% 
  group_by(restaurant) %>% 
  summarise(avg_sat_fat= mean(sat_fat)) %>% 
  filter(avg_sat_fat>10) %>% 
  summarise(num_rest=n())
Q5


```





